Spatial Reasoning and Statistical Graphics

### 2014-11-03 Paper/Draft1/TestingVisualAptitude.Rnw
Binary and extra appendix section

<<linearmodel, results='hide'>>=
pca2 <- prcomp(ans.summary[,c("card_rot", "fig_class", "folding", "vis_search")], scale=T, retx=T)
ans.model <- data.frame(ans.summary, data.frame(pca2$x))
# exclude all variables that are not supposed to go into the linear model
# those are the unrotated tests; instead we have the PCs
excl <- c("id", "card_rot", "fig_class", "folding", "vis_search", "vidgame_hrs", "major1", "major2", "minor1", "minor2", "learning_disability", "colorblind", "epilepsy", "normal_vision")

>>>>

\section{Linear Model}
<<linearmodel, results='hide'>>=
pca2 <- prcomp(ans.summary[,c("card_rot", "fig_class", "folding", "vis_search")], scale=T, retx=T)
ans.model <- data.frame(ans.summary, data.frame(pca2$x))
# exclude all variables that are not supposed to go into the linear model
# those are the unrotated tests; instead we have the PCs
excl <- c("id", "card_rot", "fig_class", "folding", "vis_search", "vidgame_hrs", "major1", "major2", "minor1", "minor2", "learning_disability", "colorblind", "epilepsy", "normal_vision")
